Kung Faux Pandas \\ \large Alternative Facts for Privacy Protection

### 2018-06-01 paper/main.tex
Auto Update from local Sharelatex

\urlstyle{same}
\title{%
  Kung Faux Pandas \\
  \large Alternative Facts for Privacy Protection}

@@

Some text about Table~\ref{included-methods}% Not sure where this table should go....

@@

>>>>

\urlstyle{same}
\title{%
  Kung Faux Pandas \\
  \large Alternative Facts for Privacy Protection %Simplifying Privacy Protection?
  }

@@

Some text about Table~\ref{included-methods} including why we built the KDE method, why DataSynthesizer, and why SGF% Not sure where this table should go....

@@

\section{Discussion}

Limitations, areas for further research:

\begin{itemize}
    \item Python module
    \item Currently don't impose any kind of result set minimum size
    \item Use in production
\end{itemize}
